Growth model analysis 3spp WB

### 2018-10-23 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added gr trends over time

load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/rawCountsAndMasses.RData")

@@

@@

```{r raw counts}
allFishBySpeciesYOY$riverOrderedGG <- factor(allFishBySpeciesYOY$river,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
allFishBySpeciesYOY$seasonGG <- factor(allFishBySpeciesYOY$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
allFishBySpeciesYOY$speciesGG <- factor(allFishBySpeciesYOY$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)

#sum across YOY
allFishBySpecies <- allFishBySpeciesYOY %>%
   group_by(river,season,year,species) %>%
   summarize( nAllFishBySpecies = sum(nAllFishBySpeciesYOY, na.rm=T),
                massAllFishBySpecies = sum(massAllFishBySpeciesYOY, na.rm=T))
allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,allFishBySpecies)

@@

ggsave('figures/3Spp_WB/rawCounts.png')

# add in sampleNumber
tmp <- d2 %>% distinct(season,year,sampleNumber)
allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,tmp)
allFish <- left_join(allFish,tmp)

@@

@@

@@

@@

tempModsTidy <- tempMods %>%
  mutate(tidy = map(model,broom::tidy)) %>%
  dplyr::select(-data,-model) %>%
  unnest() %>%
  filter( term == 'year') %>%
  mutate( sig = ifelse(p.value < 0.05,"*",""))

d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
  summarize(meanT = mean(meanTemperature, na.rm=T),
            sdT = sd(meanTemperature, na.rm=T)) %>%
  filter(riverOrderedGG == "West Brook") %>%
  ggplot( aes(year,meanT) ) +
  geom_smooth(method = 'lm', se=F, color = 'darkgrey') +
  geom_point(  ) +
  geom_line() +
  geom_errorbar( aes(ymin = meanT - sdT, ymax = meanT + sdT, width = 0.33 ) ) +
  labs( x = "Year", y = "Stream temperature (C)" ) +
  geom_text(data=tempModsTidy %>% filter(riverOrderedGG == "West Brook"),aes(x=2000.5,y=17.5, label=paste(round(estimate,2),sig))) +
  theme_publication() +
  facet_wrap(~seasonGG)

ggsave('figures/3Spp_WB/temp.png')
```

@@

cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
  filter(isYOY == 1) %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T)) %>%
  filter(riverOrderedGG == "West Brook") %>%
ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
  geom_point( position = pd, size = 2 ) +
  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
  ggtitle( "isYOY = 1" ) +
  labs( x = "Season", y = "Growth rate (mm/d)" ) +
  #scale_x_continuous( breaks = 1997:2015 ) +
  theme_publication() +
  theme( panel.grid.minor = element_blank() ) 
#  facet_wrap( ~ riverOrderedGG)

ggsave('figures/3Spp_WB/meanGRYOY1.png', width = 7, height = 7, units='in')

cd %>% group_by(speciesGG,riverOrderedGG,seasonGG) %>%
  filter(isYOY == 2) %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T)) %>%
  filter(riverOrderedGG == "West Brook") %>%
ggplot( aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
  geom_point( position = pd,size = 2 ) +
  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
  ggtitle( "isYOY = 2" ) +
  labs( x = "Season", y = "Growth rate (mm/d)" ) +
  #scale_x_continuous( breaks = 1997:2015 ) +
  theme_publication() +
  theme( panel.grid.minor = element_blank() ) 
#  facet_wrap( ~ riverOrderedGG)

ggsave('figures/3Spp_WB/meanGRYOY2.png', width = 7, height = 7, units='in')

# mean growth by species
```

@@

cd %>% group_by(species) %>% filter(riverOrderedGG == "West Brook") %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.182/.197 #bkt/bnt
.151/.197 #ats/bnt

cd %>% group_by(isYOY) %>% filter(riverOrderedGG == "West Brook") %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.120/.226 #adult/yoy
.226/.120

cd %>% group_by(season) %>% filter(riverOrderedGG == "West Brook") %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.437/((.0876+.0866+.0485)/3)
```

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
  ggplot(p, aes(year,invlogit(est),color=factor(species))) + geom_point() + facet_grid( season ~ isYOY)

  # seem to need to run the ggsave outside of markdown by pasting into console
   ggsave('figures/3Spp_WB/p.png')

@@

@@

ggplot(rHat[["ats"]], aes(beta,rHat)) +
  geom_point() +
  facet_grid(river+isYOY~season)

@@

grInt <- list()
grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")

@@

@@

  probs <- c(0.05,0.1,0.5,0.9,0.95)
  q <- grInt[[sppToPlot]] %>%
    group_by(isYOY,season,river) %>%
    summarize(
      p = list(probs),
      q = list(quantile(int,probs))
    ) %>%
    unnest() %>%
    spread(key = p, value = q)

@@

    gg <- ggplot(p %>% filter(river=='west brook'), aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(seasonGG), shape = factor(isYOY))) + 
        theme_publication() +  
        geom_point(size = 3) +
        geom_segment(aes(x = intByDay, xend = intByDayUp, yend = reorder(parameter, intByDay)), 
        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
        geom_segment(aes(x = intByDay, xend = intByDayDown, yend = reorder(parameter, intByDay)), 
        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
        xlim(c(-0.00,0.55)) +
        xlab("Mean daily growth (mm/d)") + ylab("Season") 
       # ggtitle(sppToPlot)

@@

  probs <- c(0.05,0.1,0.5,0.9,0.95)
  q <- sigmaInt[[sppToPlot]] %>%
    group_by(isYOY,season,river) %>%
    summarize(
      p = list(probs),
      q = list(quantile(int,probs))
    ) %>%
    unnest() %>%
    spread(key = p, value = q)

@@

    gg <- ggplot(p %>% filter(river == 'west brook'), aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(season), shape = factor(isYOY))) + 
        theme_publication() +  
        geom_point(size = 3) +
        geom_segment(aes(x = exp(int), xend = exp(intUp), yend = reorder(parameter, int)), 
        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
        geom_segment(aes(x = exp(int), xend = exp(intDown), yend = reorder(parameter, int)), 
        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
        #xlim(c(-0.0015,0.01)) +
        xlab("Standard deviation of daily growth (mm/d)") + ylab("Season") 
       # ggtitle(sppToPlot)

@@

```{r}
#riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)

>>>>

load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/ddddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/rawCountsAndMasses.RData")

@@

```{r count summaries for MS}

ddGInAll <- rbind(ddGIn2[[1]],ddGIn2[[2]],ddGIn2[[3]]) %>%
  filter(year %in% 2000:2015, river == 'west brook') %>%
  mutate( consecOcc = ifelse( is.na(grLength), 0,1 ) )

ddGInAll %>%
  group_by(river,species) %>%
  distinct(tag) %>%
  summarize( n = n() )

#   species     n
#   <chr>   <int>
# 1 ats      5032
# 2 bkt      8556
# 3 bnt      6389

ddGInAll %>%
  group_by(river,species) %>%
  summarize( n = n() )

#   species     n
#   <chr>   <int>
# 1 ats     15791
# 2 bkt     18412
# 3 bnt     16510

ddGInAll %>%
  group_by(river,species,enc) %>%
  summarize( n = n() )

#   species   enc     n
#   <chr>   <dbl> <int>
# 1 ats         0  3515
# 2 ats         1 12276
# 3 bkt         0  3464
# 4 bkt         1 14948
# 5 bnt         0  3855
# 6 bnt         1 12655

ddGInAll %>%
  group_by(river,species,consecOcc) %>%
  summarize( n = n() ) %>%
  spread(consecOcc,n, sep="_") %>%
  mutate( prop0 = consecOcc_0/(consecOcc_0+consecOcc_1),
          prop1 = 1 - prop0)

#   river       species consecOcc_0 consecOcc_1 prop0 prop1
# 5 west brook  ats           10203        5588 0.646 0.354
# 6 west brook  bkt           13631        4781 0.740 0.260
# 7 west brook  bnt           12420        4090 0.752 0.248

length(unique(ddGInAll$sampleNumber))

```{r table of estimated abundances}

ddGIn2[['bkt']] %>%
  filter(river == 'west brook') %>%
  distinct(river,year,season,nAllFishBySpeciesPBKT,nAllFishBySpeciesPBNT,nAllFishBySpeciesPATS) %>%
  arrange(year, season)

@@

```{r adjusted counts}
allFishBySpeciesYOY$riverOrderedGG <- factor(allFishBySpeciesYOY$river,
                         levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"), ordered = T)
allFishBySpeciesYOY$seasonGG <- factor(allFishBySpeciesYOY$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
allFishBySpeciesYOY$speciesGG <- factor(allFishBySpeciesYOY$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)

#sum across YOY
allFishBySpecies <- allFishBySpeciesYOY %>%
   group_by(river,season,year,species) %>%
   summarize( nAllFishBySpecies = sum(nAllFishBySpeciesYOY, na.rm=T),
                massAllFishBySpecies = sum(massAllFishBySpeciesYOY, na.rm=T))
allFishBySpecies$seasonGG <- factor(allFishBySpecies$season, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,allFishBySpecies)

@@

ggsave('figures/3Spp_WB/counts.png')

ggplot(allFishBySpeciesYOY %>% filter(riverOrderedGG == "West Brook", year >=2000), aes(year,nAllFishBySpecies)) +
  geom_point(aes(color = speciesGG), size=3) +
#  geom_line(aes(color = speciesGG)) +
  geom_smooth(aes(color = speciesGG), se=FALSE,method='lm') +
  geom_line( data = allFish %>% filter(riverOrderedGG == "West Brook", year >=2000), aes(year,nAllFish), size=1.25, color='darkgrey', linetype = 5 ) +
  scale_y_continuous(limits = c(0,NA)) +
  theme_publication() +
  labs( x = "Year", y = "Estimated abundance" ) +
  scale_color_grey(start = 0, end = 0.9) +
  facet_wrap( ~ seasonGG , scales = "free_y" )

ggsave('figures/3Spp_WB/countsWSlope.png', width = 11, height = 9, units='in')

nSlopes <- allFishBySpeciesYOY %>%
  filter(riverOrderedGG == "West Brook", year >=2000) %>%
  group_by( species,  season ) %>%
  nest()

nModel <- function(df){
  lm( nAllFishBySpecies ~ year, data = df )
}

nSlopes <- nSlopes %>%
  mutate( model = map(nSlopes$data, nModel) )

nSlopesTidy <- nSlopes %>%
  mutate( glance = map(model, broom::tidy)) %>% 
  unnest(glance, .drop = TRUE) %>%
  filter( term == 'year')

save(nSlopesTidy,file = 'D:/projects/linkedModels/data/out/nSlopesTidy.RData')
########################
# add in sampleNumber
tmp <- d2 %>% distinct(season,year,sampleNumber)
allFishBySpeciesYOY <- left_join(allFishBySpeciesYOY,tmp)
allFish <- left_join(allFish,tmp)

@@

```{r Table 1 - sample summary}

# sample summary table
summaryTable <- allFishBySpecies %>% 
          select(-massAllFishBySpecies) %>% 
          filter(river == 'west brook', year %in% 2000:2015) %>% 
          spread(species,nAllFishBySpecies) %>% 
          arrange(year,seasonGG)

write.csv(summaryTable, file = 'D:/projects/linkedModels/tables/rawCounts.csv')

@@

```{r mean lengths}

# Has mean size changed over time?
means <- 
  cd %>% mutate( age = year - cohort ) %>%
    filter( riverOrdered == 'west brook', ageInSamples %in% 1:10, age < 3, year < 2016 ) %>%
    group_by(species,ageInSamples,year,season,age) %>%
    summarize(meanLen = mean(observedLength,na.rm = TRUE),
              sdLen = sd(observedLength,na.rm = TRUE),
              meanGR = mean(grLength,na.rm = TRUE),
              sdGR = sd(grLength,na.rm = TRUE)
              )

lenSlopes <- means %>%
  group_by( species, ageInSamples, season, age ) %>%
  nest()

lengthModel <- function(df){
  lm( meanLen ~ year, data = df )
}

grModel <- function(df){
  lm( meanGR ~ year, data = df )
}

lenSlopes <- lenSlopes %>%
  mutate( model = map(lenSlopes$data, lengthModel),
          modelGR = map(lenSlopes$data, grModel))

###################################
######### len here, gr below ######
lenSlopesTidy <- lenSlopes %>%
  mutate(glance = map(model, broom::tidy)) %>% 
  unnest(glance, .drop = TRUE) %>%
  filter(term == 'year') %>%
  mutate( sig = ifelse(p.value < 0.05,"*","")) %>%
  mutate( sig = ifelse(p.value < 0.001,"**",sig)) %>%
  mutate( sig = ifelse(p.value < 0.0001,"***",sig))

save(lenSlopesTidy,file = 'D:/projects/linkedModels/data/out/lenSlopesTidy.RData')
##
means$seasonGG <- factor(means$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
means$speciesGG <- factor(means$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
lenSlopesTidy$seasonGG <- factor(lenSlopesTidy$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
lenSlopesTidy$speciesGG <- factor(lenSlopesTidy$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)

ggplot( means %>% filter(year >= 2000, species != 'ats'), aes(year,meanLen, group= speciesGG)) +
  geom_point( aes(color = speciesGG), size = 4) +
  geom_smooth( aes(color = speciesGG), se = FALSE, method = 'lm') +
  labs( x = "Year", y = "Mean body length (mm)" ) +
  # geom_text(data = lenSlopesTidy %>% filter(species == 'bkt'), aes(x=1999,y=220, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  # geom_text(data = lenSlopesTidy %>% filter(species == 'bnt'), aes(x=1999,y=200, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  # geom_text(data = lenSlopesTidy %>% filter(species == 'ats'), aes(x=1999,y=180, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  geom_text(data = lenSlopesTidy %>% filter(species == 'bkt', age<2), aes(x=2000,y=225, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
  geom_text(data = lenSlopesTidy %>% filter(species == 'bnt', age<2), aes(x=2000,y=203, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
#  geom_text(data = lenSlopesTidy %>% filter(species == 'ats', age<2), aes(x=2000,y=181, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +

    geom_text(data = lenSlopesTidy %>% filter(species == 'bkt', age==2), aes(x=2012.5,y=104, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
  geom_text(data = lenSlopesTidy %>% filter(species == 'bnt', age==2), aes(x=2012.5,y=82, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
#  geom_text(data = lenSlopesTidy %>% filter(species == 'ats', age==2), aes(x=2012.5,y=80, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75) +
  facet_grid(seasonGG~age)

ggsave(paste0('figures/3Spp_WB/meanLengths.png'), width = 11, height = 11, units='in')

# mean increases 
lenSlopesTidy %>%
  filter(species != 'ats') %>%
  summarise( means = mean(estimate),
             sd = sd(estimate))

# mean increases by species
lenSlopesTidy %>%
  group_by(species) %>%
  summarise( means = mean(estimate),
             sd = sd(estimate))

# do increases (slopes) increase over age? Yes
ggplot(lenSlopesTidy %>% filter(species != 'ats'), aes((ageInSamples),estimate, color=speciesGG)) +
  geom_point(aes( shape = factor(seasonGG)), size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean body length over years" ) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75)

ggsave(paste0('figures/3Spp_WB/meanLengthsOverAge.png'), width = 6, height = 6, units='in')

summary(lm(estimate~ageInSamples, data = lenSlopesTidy %>% filter(species=='bkt')))
summary(lm(estimate~ageInSamples, data = lenSlopesTidy %>% filter(species=='bnt')))

#########################
#### gr here, len above

grSlopesTidy <- lenSlopes %>%
  mutate(glance = map(modelGR, broom::tidy)) %>% 
  unnest(glance, .drop = TRUE) %>%
  filter(term == 'year') %>%
  mutate( sig = ifelse(p.value < 0.05,"*","")) %>%
  mutate( sig = ifelse(p.value < 0.001,"**",sig)) %>%
  mutate( sig = ifelse(p.value < 0.0001,"***",sig))

save(grSlopesTidy,file = 'D:/projects/linkedModels/data/out/grSlopesTidy.RData')
##
means$seasonGG <- factor(means$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
means$speciesGG <- factor(means$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
grSlopesTidy$seasonGG <- factor(grSlopesTidy$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
grSlopesTidy$speciesGG <- factor(grSlopesTidy$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)

ggplot( means %>% filter(year >= 2000, species != 'ats'), aes(year,meanGR, group= speciesGG)) +
  geom_point( aes(color = speciesGG), size = 4) +
  geom_smooth( aes(color = speciesGG), se = FALSE, method = 'lm') +
  labs( x = "Year", y = "Mean growth rate (mm/d)" ) +
  # geom_text(data = grSlopesTidy %>% filter(species == 'bkt'), aes(x=1999,y=220, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  # geom_text(data = grSlopesTidy %>% filter(species == 'bnt'), aes(x=1999,y=200, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  # geom_text(data = grSlopesTidy %>% filter(species == 'ats'), aes(x=1999,y=180, label=paste(round(estimate,2),round(p.value,4)), color = speciesGG)) +
  geom_text(data = grSlopesTidy %>% filter(species == 'bkt', age<2), aes(x=2000,y=0.7, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
  geom_text(data = grSlopesTidy %>% filter(species == 'bnt', age<2), aes(x=2000,y=0.6, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
#  geom_text(data = grSlopesTidy %>% filter(species == 'ats', age<2), aes(x=2000,y=181, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +

    geom_text(data = grSlopesTidy %>% filter(species == 'bkt', age==2), aes(x=2011.5,y=0.66, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
  geom_text(data = grSlopesTidy %>% filter(species == 'bnt', age==2), aes(x=2011.5,y=0.56, label=paste(round(estimate,4),sig)),hjust = 0)+#, color = speciesGG)) +
#  geom_text(data = grSlopesTidy %>% filter(species == 'ats', age==2), aes(x=2012.5,y=80, label=paste(round(estimate,2),sig)),hjust = 0)+#, color = speciesGG)) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75) +
  facet_grid(seasonGG~age)

ggsave(paste0('figures/3Spp_WB/meanGRs.png'), width = 11, height = 11, units='in')

# mean increases 
grSlopesTidy %>%
  filter(species != 'ats') %>%
  summarise( means = mean(estimate),
             sd = sd(estimate))

# mean increases by species
grSlopesTidy %>%
  group_by(species) %>%
  summarise( means = mean(estimate),
             sd = sd(estimate))

# do increases (slopes) increase over age? Yes
ggplot(grSlopesTidy %>% filter(species != 'ats'), aes((ageInSamples),estimate, color=speciesGG)) +
  geom_point(aes( shape = factor(seasonGG)), size = 3) +
  geom_smooth(method='lm', se=FALSE) +
  scale_x_continuous(breaks = 1:10, labels = c(0,0,1,1,1,1,2,2,2,2)) +
  labs( x = "Age", y = "Slope of mean growth rate over years" ) +
  theme_publication() +
  scale_color_grey(start = 0.15, end = 0.75)

ggsave(paste0('figures/3Spp_WB/meanGRsOverAge.png'), width = 6, height = 6, units='in')

summary(lm(estimate~ageInSamples, data = grSlopesTidy %>% filter(species=='bkt')))
summary(lm(estimate~ageInSamples, data = grSlopesTidy %>% filter(species=='bnt')))

@@

lmFunctionF <- function(df){ lm( meanF ~ year, data=df ) }

flowMods <- d2 %>%
  group_by(riverOrderedGG,seasonGG,year) %>%
  summarize(meanF = mean(meanFlow, na.rm=T),
            sdF = sd(meanFlow, na.rm=T)) %>%
  group_by( riverOrderedGG, seasonGG ) %>%
  nest() %>%
  mutate( model = map(data,lmFunctionF) )

flowSlopesTidy <- flowMods %>%
  mutate(tidy = map(model,broom::tidy)) %>%
  dplyr::select(-data,-model) %>%
  unnest() %>%
  filter( term == 'year') %>%
  mutate( sig = ifelse(p.value < 0.05,"*",""))

save(flowSlopesTidy,file = 'D:/projects/linkedModels/data/out/flowSlopesTidy.RData')

#################

@@

tempSlopesTidy <- tempMods %>%
  mutate(tidy = map(model,broom::tidy)) %>%
  dplyr::select(-data,-model) %>%
  unnest() %>%
  filter( term == 'year') %>%
  mutate( sig = ifelse(p.value < 0.05,"*",""))

d2 %>% group_by(riverOrderedGG,seasonGG,year) %>%
  summarize(meanT = mean(meanTemperature, na.rm=T),
            sdT = sd(meanTemperature, na.rm=T)) %>%
  filter(riverOrderedGG == "West Brook") %>%
  ggplot( aes(year,meanT) ) +
  geom_smooth(method = 'lm', se=F, color = 'darkgrey') +
  geom_point( size = 3 ) +
  geom_line() +
  geom_errorbar( aes(ymin = meanT - sdT, ymax = meanT + sdT, width = 0.33 ) ) +
  labs( x = "Year", y = "Stream temperature (C)" ) +
  geom_text(data=tempSlopesTidy %>% filter(riverOrderedGG == "West Brook"),aes(x=2000.5,y=17.5, label=paste(round(estimate,2),sig))) +
  theme_publication() +
  facet_wrap(~seasonGG)

ggsave('figures/3Spp_WB/temp.png')

save(tempSlopesTidy,file = 'D:/projects/linkedModels/data/out/tempSlopesTidy.RData')

@@

growthYOY <- 
cd %>% group_by(speciesGG,species,riverOrderedGG,seasonGG,isYOY) %>%
  filter( riverOrdered == 'west brook', year < 2016, species != 'ats' )  %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))

ggplot(growthYOY%>%filter(isYOY == 1), aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
  geom_point( position = pd, size = 3 ) +
  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
  ggtitle( "isYOY = 1" ) +
  labs( x = "Season", y = "Growth rate (mm/d)" ) +
  #scale_x_continuous( breaks = 1997:2015 ) +
  scale_color_grey(start = 0.0, end = 0.5) +
  theme_publication() +
  theme( panel.grid.minor = element_blank() ) 
#  facet_wrap( ~ riverOrderedGG)

ggsave('figures/3Spp_WB/meanGRYOY1.png', width = 4, height = 4, units='in')

ggplot(growthYOY%>%filter(isYOY == 2), aes(seasonGG,meanGR, color=speciesGG, shape=speciesGG) ) +
  geom_point( position = pd, size = 3 ) +
  geom_errorbar( aes(ymin = meanGR - sdGR, ymax = meanGR + sdGR), width = 0.33, position=pd ) +
  ggtitle( "isYOY = 2" ) +
  labs( x = "Season", y = "Growth rate (mm/d)" ) +
  #scale_x_continuous( breaks = 1997:2015 ) +
  scale_color_grey(start = 0.0, end = 0.5) +
  theme_publication() +
  theme( panel.grid.minor = element_blank() )

ggsave('figures/3Spp_WB/meanGRYOY2.png', width = 4, height = 4, units='in')

# get ratios of growth rates for the 2 species
growthYOYWide <- growthYOY %>% ungroup() %>% select(-sdGR,-speciesGG) %>% spread(key=species,value=meanGR) %>%
  mutate(ratio = bnt/bkt)

mean(growthYOYWide$ratio)
# 1.107745

@@

cd %>% group_by(species) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.197/.182#bnt/bkt

cd %>% group_by(isYOY) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.145/.244 #adult/yoy
.244/.145

cd %>% group_by(season) %>% filter(riverOrderedGG == "West Brook",species != 'ats') %>%
  summarize(meanGR = mean(grLength, na.rm=T),
            sdGR = sd(grLength, na.rm=T))
.434/((.114+.124+.067)/3)
```

@@

  p <- array2df(ddD$q50$pBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1)

  p$speciesGG <- factor(p$species, levels = 1:3, labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
  p$seasonGG <- factor(p$season, levels = 1:4, labels = c("Spring","Summer","Autumn","Winter"), ordered = T)
  p$isYOYGG <- factor(p$isYOY, levels = 1:2, labels = c("Juvenile","Adult"), ordered = T)

  ggplot(p, aes(year,invlogit(est),color=factor(speciesGG))) + 
    geom_point(size = 2) + 
    labs( x = 'Year', y = 'Probability of detection') +
    scale_color_grey(start = 0.0, end = 0.85) +
    theme_publication() +
    facet_grid( seasonGG ~ isYOYGG)

  # seem to need to run the ggsave outside of markdown by pasting into console
   ggsave('figures/3Spp_WB/p.png', height = 11, width = 9, units = 'in')

@@

rBkt <- unlist(mcmc[['bkt']]$Rhat)
sort(rBkt[rBkt > 1.1])

rBnt <- unlist(mcmc[['bnt']]$Rhat)
sort(rBnt[rBnt > 1.1])
mcmc[['bnt']]$Rhat$grBeta[,,,1]
mcmc[['bnt']]$Rhat$grInt
mcmc[['bnt']]$Rhat$grIntMu

@@

hist(rHat[["bkt"]]$rHat)
hist(rHat[["bnt"]]$rHat)
rHat[["bnt"]] %>% filter( rHat >1.1 )

ggplot(rHat[["bkt"]], aes(beta,rHat)) +
  geom_point() +
  facet_grid(river+isYOY~season)

@@

grInt <- list()
grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>% mutate(species = 'bkt')
grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int") %>%   mutate(species = 'bnt')
grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int") %>% mutate(species = 'ats')

@@

#grIntDF <- rbind(grInt[['bkt']],grInt[['bnt']],grInt[['ats']])
#tmp <- grIntDF %>% filter(river == 'west brook')
#save(tmp , file= "data/out/grIntDFAllIters.RData") #for Ron

@@

  probs <- c(0.025,0.1,0.5,0.9,0.975)
  q <- grInt[[sppToPlot]] %>%
    group_by(isYOY,season,river) %>%
    summarize(
      p = list(probs),
      q = list(quantile(int,probs))
    ) %>%
    unnest() %>%
    spread(key = p, value = q)

@@

  #save(p, file= paste0("data/out/allInts_",sppToPlot,".RData"))  #for projections and tables

    gg <- ggplot(p %>% filter(river=='west brook'), aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(isYOY), shape = factor(isYOY))) + 
        theme_publication() +  
        geom_point(size = 4) +
        geom_segment(aes(x = intByDay, xend = intByDayUp, yend = reorder(parameter, intByDay)), 
        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
        geom_segment(aes(x = intByDay, xend = intByDayDown, yend = reorder(parameter, intByDay)), 
        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
        xlim(c(-0.00,0.55)) +
        xlab("Mean daily growth (mm/d)") + ylab("Season") +
        scale_color_grey(start = 0, end = 0.65) 
       # ggtitle(sppToPlot)

@@

  probs <- c(0.025,0.1,0.5,0.9,0.975)
  q <- sigmaInt[[sppToPlot]] %>%
    group_by(isYOY,season,river) %>%
    summarize(
      p = list(probs),
      q = list(quantile(int,probs))
    ) %>%
    unnest() %>%
    spread(key = p, value = q)

@@

    gg <- ggplot(p %>% filter(river == 'west brook'), aes(x = exp(int), y = reorder(parameter,int,na.rm=TRUE), color = factor(isYOY), shape = factor(isYOY))) + 
        theme_publication() +  
        geom_point(size = 3) +
        geom_segment(aes(x = exp(int), xend = exp(intUp), yend = reorder(parameter, int)), 
        size = 0.5, arrow = arrow(angle = 90, length = unit(0.05, "inches"))) + 
        geom_segment(aes(x = exp(int), xend = exp(intDown), yend = reorder(parameter, int)), 
        size = 0.5,arrow = arrow(angle = 90, length = unit(0.05, "inches"))) +
        #xlim(c(-0.0015,0.01)) +
        xlab("Standard deviation of daily growth (mm/d)") + ylab("Season") +
        scale_color_grey(start = 0, end = 0.65) 
       # ggtitle(sppToPlot)

@@

```{r grInt}
#riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)
